### 2022-04-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@5e66493683d008c6662dbbd79b7ddd910f641b51 🚀

In this paper, we examine the biogeographic structure of
bats-betacoronaviruses associations, based on a curated dataset of known
and recently discovered hosts. This work is important both as a
description of the bats-betacoronavirus complex, but aslo because more
broadly, bats are known reservoirs for a variety of emerging viruses
(Calisher 2006), making balancing the needs for bat conservation and
disease prevention a potentially difficult act and a source of
human-wildlife conflicst, especially in more densely populated areas
(REF). By drawing on concepts from the Geographic Mosaic Theory of
Coevolution (REF), we turn these associations into a spatially explicit
additive mapping of zoonotic risk components, which reveals extreme
heterogeneity of risk at the global scale; furthermore, we identify the
Amazon and South-Eastern Asia as hotspots of phylogenetic
distinctiveness of betacoronaviruses; surprisingly, current data suggest
that viral sharing between hosts in high in the Amazon and low in
South-Eastern Asia, which has the potential to result in different
evolutionary dynamics between these two regions.

@@

@@

@@

@@

>>>>

In this paper, we examine the biogeographic structure of
bats-betacoronaviruses associations, based on a curated dataset of known
and recently discovered hosts. This work is important both as a
description of the bats-betacoronavirus complex, but aslo because more
broadly, bats are known reservoirs for a variety of emerging viruses and
pathogens (Calisher et al. 2006, Melaun et al. 2014), making balancing
the needs for bat conservation and disease prevention a potentially
difficult act and a source of human-wildlife conflicts, especially in
more densely populated areas (Stone et al. 2015, Rego et al. 2015). By
drawing on concepts from the Geographic Mosaic Theory of Coevolution
(Thompson 2005), we turn these associations into a spatially explicit
additive mapping of zoonotic risk components, which reveals extreme
heterogeneity of risk at the global scale; furthermore, we identify the
Amazon and South-Eastern Asia as hotspots of phylogenetic
distinctiveness of betacoronaviruses; surprisingly, current data suggest
that viral sharing between hosts in high in the Amazon and low in
South-Eastern Asia, which has the potential to result in different
evolutionary dynamics between these two regions.

@@

\leavevmode\hypertarget{ref-Calisher2006BatImp}{}%
Calisher, C. H. et al. 2006. Bats: Important Reservoir Hosts of Emerging
Viruses. - Clinical Microbiology Reviews 19: 531--545.

@@

\leavevmode\hypertarget{ref-Melaun2014BatPot}{}%
Melaun, C. et al. 2014. Bats as Potential Reservoir Hosts for
Vector-Borne Diseases. - In: Klimpel, S. and Mehlhorn, H. (eds), Bats
(Chiroptera) as Vectors of Diseases and Parasites: Facts and Myths.
Parasitology Research Monographs. Springer, pp. 25--61.

@@

\leavevmode\hypertarget{ref-Rego2015AssHum}{}%
Rego, K. M. da C. et al. 2015. Assessing human-bat interactions around a
protected area in northeastern Brazil. - Journal of Ethnobiology and
Ethnomedicine 11: 80.

@@

\leavevmode\hypertarget{ref-Stone2015ManCon}{}%
Stone, E. et al. 2015. Managing Conflict between Bats and Humans: The
Response of Soprano Pipistrelles (Pipistrellus pygmaeus) to Exclusion
from Roosts in Houses. - PLoS ONE 10: e0131825.

\leavevmode\hypertarget{ref-Thompson2005GeoMos}{}%
Thompson, J. N. 2005. The Geographic Mosaic of Coevolution. - University
Of Chicago Press.
